\LARGE \bf Efficient Sampling for Grasp Quality Evaluation with Gaussian Process Implicit Surface Representation

### 2014-09-17 paper.tex
fixed introduction and added related work

\todo{Write a better Intro, needs to have a better sell}
Many modern 3d sensors give noisy point clouds as output, so shape uncertainty is a common problem \cite{singhbigbird}. As shown in Fig. \ref{fig:noisy data}, the noise in our measurements of object shape can greatly change the surface normals and contact points, which are the parameters that most grasp metrics rely on.  A number of metrics have been proposed to evaluate form and force closure with scalar quality measures for grasping \cite{bicchi2000}.   However, only recently have people started looking into a metric's robustness to uncertainty.

We use Gaussian Processes \cite{rasmussen2006} to convert the point cloud measurements into an implicit surface with uncertainty in the shape. Gaussian Processes provide a formal way to incorporate uncertainty, however this sophisticated representation presents new challenges for evaluating the expected grasp quality. The wrench-space Ferrari-Canny force closure quality measure \cite{ferrari1992} calculates the maximum disturbance that can be resisted given bounds on the contact forces.

@@

We also treat the problem of finding the best grasp in a set of proposed grasps as a n-arm bandit problem and propose an $\epsilon$ - greedy policy for finding the best grasp in the set in an anytime like manner.

@@

\section{Related Work}

While a variety of grasp metrics have been proposed, few explicitly looked at uncertainty in grasp parameters. Zheng et al. looked at friction and contact point uncertainty \cite{zheng2005}. He computed the maximum distance a contact point was allowed to deviate from its expected grasp, while maintaining force closure. Kehoe et al. looked at shape uncertainty for push grasps, however this was limited to parallel jaw grippers and only measured the probability of force closure \cite{kehoe2012toward}. More closely related to our approach is the work of Christopoulos and Schrater \cite{christopoulos2007handling}. They use a spline representation for uncertainty and measure the probability of losing force closure, their approach though is limited to two contacts. Our method looks at not only force closure, but provides the quality of the expected grasp and an upper bound on the expexted change from that quality.

>>>>

A robot in the wild is expected to encounter an object, grasp and manipulate it. In order to do so it must use its noisy sensor data to build a model of the object, for which to plan grasps on. While most grasp planning algorithms currently assume a polygonal mesh \cite{grasp_it}, their is no easy way to handle the uncertainty associated with partial visibility, sensor noise and surface properties such as specularity and transparency. We thus propose a Bayesian approach to this problem to formally go from point cloud to an uncertainty representation using Gaussian Processes.

An alternative to polygonal mesh representation is the signed distance field, which is zero-valued at the object surface, positive valued outside the object, and negative valued in the object interior \cite{newcombe2011kinectfusion}. We look at encoding uncertainty into this model with a Bayesian representation known as Gaussian Process Implicit Surface (GPIS). The key idea behind GPIS is to represent shape uncertainty as a distribution overall possible SDFs that could represent the shape. For example, GPIS-based models have large variance where data is known to be unreliable (e.g. occlusions, specularities) and lower variance where measurements are more reliable.

 While a GPIS is a formal method for representation of uncertainty and can offer continuous function that can be used for local grasp optimization \cite{jeff_paper}. Evaluation of grasp quality through techniques like Monte-Carlo Integration on a GPIS requires an exhaustive sampling of SDFs, which is extremely computationally expensive and not suited for a real time application. We purpose an alternative to sampling SDFs by computing a distribution on explicit grasp parameters and performing Monte-Carlo integration on that instead.

@@

To further improve the efficiency of grasp quality evaluation, for a given set of grasps. We demonstrate that formulating the problem as an n-arm bandit problem allows us to formulate a policy that intelligently select which grasps to sample next. N-arm bandit problems look at the situation of an agent being presented with N slot machines, where each slot machine gives a reward from some unknown distribution. The goal of the agent is to efficiently explore the slot machines and then maximize reward by exploiting the best one. In our problem each lever pull is an evaluation of a grasp metric (e.g. Ferrari-Canny), which is computationally expensive. Thus finding a policy to minimize evaluations is essential for real time applications.

@@

\section{Related Work}
Many different methods for representing objects exist, most of which were developed in the graphics community for making rendering and simulations computationally tractable; see \cite{van2014computer} for an overview. Polygonal mesh models are the most common representation in robotics but these models usual assume perfectly known geometry. Extension of mesh models to include  uncertainty generally assume independent noise on the vertex locations, ignoring noise correlation \cite{kehoe2012toward}. As an alternative, implicit surface representations are becoming increasingly popular in robotics due to their success in real-time surface modeling from range images \cite{curless1996volumetric},\cite{newcombe2011kinectfusion}, \cite{hornung2013octomap}. These representation include a confidence estimate based on a sensor noise model, but they cannot estimate the location in the surface regions where no measurements were obtained or represent correlations between voxels \cite{curless1996volumetric}.

Choosing grasps given a surface representation of an object usually focuses on improving grasps for a  object shape \cite{ferrari1992}. Past work on grasping has focused on state uncertainty \cite{goldberg1990bayesian}\cite{goldberg1990stochastic} \cite{stulp2011learning},  uncertainty in object pose \cite{christopoulos2007handling}  \cite{felip2009robust} \cite{kim2012physically} or uncertainty in the location of contact with the object \cite{zheng2005}. Robust grasp selection for parallel jaw grippers on uncertain shapes was studied by Kehoe et al. for both zero-slip push grasps \cite{kehoe2012toward} and slip push grasps \cite{kehoe2012estimating} using Monte Carlo integration for the expected grasp quality, but this assumed extruded polygons with independent noise at each vertex. Christopoulus et al. sampled spline fits for 2-dimensional planar objects to measure the quality of uncertainity, but did not have a formal method for representing uncertainity and only calculated the probability of achieving force closure. .
